\input{annales.sty}
\versionCompil


\input{./sources/preamble}
\input{./sources/preamble2}

\begin{document}
\input{./sources/titlepage}

% \raggedbottom
\titre{Asymptotics on Lempel-Ziv'78 compression}
\abstract{Diving into universal data compression through the analysis of the
Lempel-Ziv'78 algorithm and other related subjects - with the help of probabilistic models, 
computer simulation,
complex analysis, and information theory.}

% \medskip
% \noindent
% \emph{Keywords:} Information theory - Data compression - LZ'78 - Complex analysis

% Veuillez ne pas modifier ce titre SVP.
\tableofcontents

\section*{Introduction}

I did my internship at Purdue University, working
at the Center for Science of Information, a lab 
dedicated to information theory research, in the 
state of Indiana but close to Chicago city.

My internship consisted in several research tasks, 
two of which involved a long-term purpose: 
going further into the analysis of the Lempel-Ziv'78 
compression scheme. I built numerical simulations
out of the probabilistic models used to describe 
this scheme, and used we used them to gain some
insights on the asymptotic behavior of some 
random variables which are key to measuring the 
efficiency of the LZ'78 compression.
This project, especially the third part with 
the tail symbols, was related to recent work by my supervisor
and his friend researcher Philippe Jacquet
towards solving a conjecture that has remained 
open for twenty years. Finally, I got to work 
on the draft of a paper by an international team -  
though mostly italian researchers - which is exploring
the efficiency of certain parsing strategies in 
data compression - particularly LZ'77 and LZ'78.

This first part of this report is to be seen as 
an introduction to the context of this research.
The second presents the fixed-length probabilistic model,
and how the simulations we have conducted indicate 
that a central limit law applies within it, while identifying
and computing an expression for the variance of a key random variable.
The third part switches to another similar model, the 
Markov independent model, in the context of which 
we conducted simulations and started doing the formal asymptotic
analysis of a covariance related to the analysis of LZ'78.
The fourth part summarizes our collaboration on the draft
regarding the analysis of an algorithm which improves 
over regular LZ'78: the Flexible Parsing algorithm.



\input{./sources/introduction}

% \section{Numerical simulation of LZ78 for Markovian sources}
\section{Central limit theorem}
\renewcommand{\subsection}{\subsubsection}
\renewcommand{\section}{\oldsubsection}
\input{./sources/rapport}
% % \input{szpan}
\input{./sources/alternative}
\renewcommand{\subsection}{\oldsubsection}
\renewcommand{\section}{\oldsection}

\section{Tail symbols analysis}
\renewcommand{\subsection}{\subsubsection}
\renewcommand{\section}{\oldsubsection}
% \section{Tail symbols definition}
% \input{./sources/tail_symbols_definition}
\input{./sources/tails}
\renewcommand{\subsection}{\oldsubsection}
\renewcommand{\section}{\oldsection}

\input{./sources/flexible}

\newpage
\section{Research at Purdue}
\input{./sources/purdue}

\bibliographystyle{plain}
\bibliography{bibzot}


\pagebreak


\input{./sources/appendices}

\end{document}
