\titre{ Multiple approaches to Lempel-Ziv compression algorithm }
% Veuillez ne pas modifier ce titre SVP.
% En cas de doute, prévenez votre coordinateur.
% Compilez par: "latex main.tex".

\tableofcontents

\newpage

\Indications
\medskip

	\centers{\textbf{Partie III}}

\begin{indications}{III.1} % Remplacer IV.A.2 par la chaîne de caractères
                            % la plus longue dans les \item

\item[III.1] For a curated list, and some visualizations, see my blog
             article \url{blog.lol}{here}.

\item[III.2] The code used to do these simulations is available 
    in this github repository \url{github.com/gliboc/markus}{here}.


\end{indications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

% Un aide-mémoire des symboles mathématiques est disponible en ligne:
% http://auteurs.h-k.fr/annales/Doc/aide-memoire/symboles-mathematiques.pdf

\section*{Introduction to Lempel-Ziv}
    \subsection*{The algorithm}

\section{On the quest for optimal compression : algorithmic improvements}
    \subsection{What can be done according to information theory}
    \subsection{Information sources}
        Memoryless (M), Markov (MS), Dynamic (DS)
        Maybe even bounded sth ?
    \subsection{Why Markov sources are good for real world case}
        Language
        Programs as finite state automata. Human usage determines
        which branches are taken, at which frequency.
    \subsection{Flexible Parsing}

\section{Combinatorial analysis applied to algorithms}
    \subsection{Mathematical tools}
        Depoissonization, Mellin transform, the matrix P(s)
        and its Frobenius eigenvalue
    \subsection{Their limits}
        The open conjecture (for 50 years) that Lempel-Ziv
        obeys CLT, although my simulations show that it is
        true with little doubt.

\section{Lempel-Ziv 78 in practice}
    \subsection{Philosophical problematics}
        Compression = knowledge contained
        This is why compression is tied to entropy etc.
    \subsection{Business problematics}
        Counterpart
        Tradeoff speed / efficiency
    \subsection{Most important implementations and use cases}
        DIVANS at Dropbox
        Brotli
        etc.
        Write a blog article comparing these algorithms,
        or find one. Use your own data generated with 
        Markov sources.
        The "modular" approach by DIVANS => write a module 
        for them with vanilla LZ78 or sth ?
        
\section{Markov sources simulation}
    \subsection{Input simulation : Markov sources}
        Difficulties, solutions
    \subsection{Related asymptotics}
    \subsection{Future results}
        Jacquet's paper 



\begin{remarque}

\noindent C'est ainsi que l'on fait une remarque hors corrigé.

\end{remarque}


% Pas de \end{document} ici: voir 'main.tex'
